---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
```{r}
unzip("activity.zip")
data <- read.csv("activity.csv")
```


## What is mean total number of steps taken per day?
Calculate the steps by day
```{r}
data$date <- as.Date(data$date)
stepsPerDay <- aggregate(data["steps"], by=data["date"], sum, na.rm=TRUE)
stepsPerDay
```
Produce a histogram of steps by date
```{r}
library(ggplot2)
ggplot(stepsPerDay, aes(x=date, y=steps)) +
    geom_bar(stat = "identity")
```
Mean and median steps
```{r}
mean(stepsPerDay$steps)
median(stepsPerDay$steps)
```

## What is the average daily activity pattern?
Time series of average steps by interval
```{r}
stepsPerInterval <- aggregate(data["steps"], by=data["interval"], sum, na.rm=TRUE)
avgStepsPerInterval <- stepsPerInterval
avgStepsPerInterval[2] <- as.numeric(as.character(stepsPerInterval$steps)) / length(unique(data$date))
ts <- ggplot(avgStepsPerInterval, aes(x=interval, y=steps)) +
    geom_line()
ts
```
The highest amount of average steps took place during the interval 835
```{r}
avgStepsPerInterval[avgStepsPerInterval$steps == max(avgStepsPerInterval$steps), ] 
```

## Imputing missing values
```{r}
sum(is.na(data$steps))
```
The 
```{r}
data[is.na(data)] <- 0
mean(stepsPerDay$steps)
median(stepsPerDay$steps)
```


## Are there differences in activity patterns between weekdays and weekends?
```{r}
library(lattice)
weekdays <- c('Monday', 'Tuesday', 'Wednesday', 'Thursday', 'Friday')
data$wDay <- factor((weekdays(data$date) %in% weekdays),
                    levels=c(FALSE, TRUE), labels=c('weekend', 'weekday'))
xyplot(steps ~ interval | wDay, data = data, layout=c(1,2), type="l")
```













